---
title: "Urine Cultures 2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
library(data.table)
library(harrypotter)
library(lubridate)
library(tictoc)
library(ggrepel)
library(knitr)
library(gridExtra)

source('cp_province.R')
source('bootstrap_test.R')

# SPAIN MAP functions
library(broom)
library(sp)
library(rgdal)
library(maptools)
library(splancs)
require(gpclib)
gpclibPermit()

simpleCap <- function(x) {
  output <- c()
  for(i in seq_along(x)){
    s <- x[[i]] %>% tolower()
    s <- strsplit(s, " ")[[1]]
    output[[i]] <- paste(toupper(substring(s, 1,1)), substring(s, 2),
          sep="", collapse=" ") 
  }
  return(output)
}

fungus_list <- c('Candida', 'Fusarium', 'Penicillum')

remove_fungus <- function(df){
  fungus_list <<- c('Candida', 'Fusarium', 'Penicillum')
  df %>% 
    filter(!(species %in% fungus_list)) %>% 
    return()
}
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}

not_all_na <- function(x)!all(is.na(x))

general <- fread('data/general.csv') %>% 
  select_if(not_all_na) %>%
  data.table()

general[, FECHA := FECHA %>% myd()]
general[, EDAD :=  EDAD %>% as.numeric()]
general[, province := CP %>% as.character() %>%  substr(start = 1, stop = 2) %>% cp_to_province()]
general[, animal :=  `PERRO/GATO` %>% as.factor() ]
general[, species1 := `ESPECIE 1`]
general[, species2 := `ESPECIE 2`]
general[, species3 := `ESPECIE 3`]
general[, season := `ESTACIÓN`]
general[, n_species := `nº ESPECIES`]
general[, infected := (species1 != '0')]
general[, ca := `C.A` %>% simpleCap() %>% 
          str_replace('C. León', 'Castilla y León') %>% 
          str_replace('C. La Mancha', 'Castilla-La Mancha') %>% 
          str_replace('Murcia', 'Región de Murcia') %>% 
          str_replace('Navarra', 'Comunidad Foral de Navarra') %>% 
          str_replace('Canarias', 'Islas Canarias') %>% 
          str_replace('Asturias', 'Principado de Asturias') %>% 
          str_replace('Baleares', 'Islas Baleares') %>% 
          str_replace('Madrid', 'Comunidad de Madrid') %>% 
          str_replace('Ceuta/meilla', 'Ceuta y Meilla') %>% 
          str_replace('Valencia', 'Comunidad Valenciana') %>% 
          str_replace('Andalucia', 'Andalucía') %>% 
          str_replace('Aragon', 'Aragón')]
general[, ca := ifelse(province == 'Madrid', 'Comunidad de Madrid', ca)]
general[, ca := ifelse(province == 'Barcelona', 'Cataluña', ca)]
general[, ca := ifelse(province == 'A Coruña', 'Galicia', ca)]
general[, ca := ifelse(province == 'Cantabria', 'Cantabria', ca)]
general[, ca := ifelse(province == 'Málaga', 'Andalucía', ca)]
general[, province := ifelse(province == 'Balearic Islands', 'Baleares', province)]

# general <- general %>% filter(!(species1 %in% fungus_list))
# general <- general %>% filter(!(species2 %in% fungus_list))
# general <- general %>% filter(!(species3 %in% fungus_list))

general <- general %>% mutate(species1 = ifelse(species1 %in% fungus_list, NA, species1))
general <- general %>% mutate(species2 = ifelse(species2 %in% fungus_list, NA, species2))
general <- general %>% mutate(species3 = ifelse(species3 %in% fungus_list, NA, species3))

general <- general %>% filter(!(species1 == 'CONTAMINACIÓN'))
general <- general %>% filter(!(species2 == 'CONTAMINACIÓN'))
general <- general %>% filter(!(species3 == 'CONTAMINACIÓN'))

```


# Summary Statistics

```{r}
general %>% 
  group_by(animal) %>% 
  summarise(n = n()) %>% 
  mutate(n = round(100 * n / sum(n), 2)) %>% 
  mutate(animal = ifelse(animal == 1, 'Dog', 'Cat')) %>% 
  na.omit() %>% 
  ggplot(aes(x = animal, y = n, fill = n)) +
  geom_col() +
  geom_label(aes(label = n %>% paste0(' %')), fill = 'white') +
  scale_fill_hp(guide = FALSE, begin = 0.3, end = 0.7) +
  xlab('') +
  ylab('(%)')

general %>% 
  group_by(animal) %>% 
  summarise(n = n()) %>% 
  mutate(animal = ifelse(animal == 1, 'Dog', 'Cat')) %>% 
  na.omit()
```




```{r}

gg1 <- general %>% 
  filter(animal == 1) %>% 
  group_by(infected) %>% 
  summarise(n = n()) %>% 
  mutate(n = n / sum(n)) %>% 
  arrange(n) %>% 
  mutate(pos = (cumsum(n) - n/2)) %>% 
  ggplot(aes(x = '', y = n, fill = infected)) +
  geom_col(position = 'fill') +
  coord_polar(theta ='y', start = 0) +
  geom_label(aes(label = (100*n) %>% round(2) %>% paste0('%'), x = 1, y = pos), 
             fill = 'white',
             size = 5.5,
             alpha = 0.7) +
  theme_void() +
  scale_fill_hp_d(option = 'Gryffindor2', name = 'Culture Result', labels = c('Negative', 'Positive'), direction = -1) +
  ggtitle('Dogs') +
  theme(plot.title = element_text(hjust = 0.5))

gg2 <- general %>% 
  filter(animal == 2) %>% 
  group_by(infected) %>% 
  summarise(n = n()) %>% 
  mutate(n = n / sum(n)) %>% 
  arrange(n) %>% 
  mutate(pos = (cumsum(n) - n/2)) %>% 
  ggplot(aes(x = '', y = n, fill = infected)) +
  geom_col(position = 'fill') +
  coord_polar(theta ='y', start = 0) +
  geom_label(aes(label = (100*n) %>% round(2) %>% paste0('%'), x = 1, y = pos), 
             fill = 'white',
             size = 5,
             alpha = 0.7) +
  theme_void() +
  scale_fill_hp_d(option = 'Gryffindor2', name = 'Culture Result', labels = c('Negative', 'Positive'), direction = -1) +
  ggtitle('Cats') +
  theme(plot.title = element_text(hjust = 0.5))


grid.arrange(gg1,gg2, ncol = 2)


general %>% 
  group_by(animal, infected) %>% 
  summarise(n = n()) %>% 
  group_by(animal) %>% 
  mutate(total = sum(n)) %>% 
  filter(infected) %>% 
  na.omit() %>% 
  mutate(infected = n, no_infected = total - n) %>% 
  ungroup() %>% 
  select(infected, no_infected) %>% 
  chisq.test()
  
```

## Number of Species Bacteria Frequency

```{r}
general %>% 
  filter(animal == 1) %>% 
  group_by(n_species) %>% 
  summarise(n = n()) %>% 
  mutate(n = 100 * n/sum(n)) %>% 
  na.omit() %>% 
  ggplot(aes(x = n_species, y = n)) +
  geom_col(fill = hp(10)[[4]], colour = 'black', size= 0.15) +
  geom_label(aes(label = n %>% round(2) %>% paste0(' %'))) +
  xlab('N Species') +
  ylab('(%)') +
  theme_bw() +
  ggtitle('Dog')

general %>% 
  filter(animal == 2) %>% 
  group_by(n_species) %>% 
  summarise(n = n()) %>% 
  mutate(n = 100 * n/sum(n)) %>% 
  na.omit() %>% 
  ggplot(aes(x = n_species, y = n)) +
  geom_col(fill = hp(10)[[7]], colour = 'black', size= 0.15) +
  geom_label(aes(label = n %>% round(2) %>% paste0(' %'))) +
  xlab('N Species') +
  ylab('(%)') +
  theme_bw() +
  ggtitle('Cat')
```



# Geographic Distribution Table

```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
prov_table <- general %>% 
  group_by(province) %>% 
  summarise(n = n(),
            infected = sum(infected)) %>%
  mutate(no_infected = n - infected ) %>% 
  mutate(proportion_infected = infected / n) %>% 
  na.omit()

prov_table %>% kable()
```

## Map

```{r echo = FALSE, warning = FALSE, message = FALSE}

sp_map <- function(level = 2){
  spmapesp <- readOGR(paste0('data/gadm36_ESP_shp/gadm36_ESP_', level,'.shp'))
  mymap <- tidy(spmapesp)
  mymap$province <-  spmapesp@data[ as.character(mymap$id), paste0("NAME_", level, "")]
  mymap$id <- factor(mymap$id)
  return(mymap)
}

mymap <- sp_map(level = 2)

general %>% 
  mutate(animal = ifelse(animal == 1, 'Dog', 'Cat')) %>% 
  group_by(province, animal) %>% 
  summarise(n = n(),
            infected = sum(infected, na.rm = TRUE)) %>% 
  group_by(animal) %>% 
  mutate(proportion_infected = 100 * infected / n) %>% 
  right_join(mymap) %>% 
  na.omit() %>% 
  ggplot(aes(x= long, y = lat, group = group, alpha = proportion_infected)) +
  geom_polygon(fill = hp(option = 'Gryffindor', n = 10)[[1]])  +
  scale_alpha_continuous(range = c(0.25,1), name = '%') +
  theme_void()

```



```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
prov_table %>% 
  dplyr::select(infected, no_infected) %>% 
  chisq.test()
```

Chi-Squared test outputs a p-value below 0.05. Thus it seems reasonable to *negate* that the proportion of infected population is homogeneously distributed across provinces.

# Batceria Species

## Frequency Table

```{r}
general %>% 
  select(species1, animal) %>% 
  set_names('species', 'animal') %>% 
  rbind(
    general %>% 
      select(species2, animal) %>% 
      set_names('species', 'animal')
  ) %>% 
  rbind(
    general %>% 
      select(species3, animal) %>% 
      set_names('species', 'animal')
  ) %>% 
  table() %>% 
  as_tibble() %>% 
  filter(species != 0) %>% 
  filter(species != '') %>%
  mutate(animal = ifelse(animal == 1, 'Dog', 'Cat')) %>% 
  dcast(species~animal, value = 'n') %>% 
  arrange(desc(Cat + Dog)) %>% 
  mutate(Dog_prop = round(Dog / sum(Dog), 2)) %>% 
  mutate(Cat_prop = round(Cat / sum(Cat), 2)) %>% 
  kable()
```


```{r echo = FALSE, warning = FALSE}
bacteris_animal <- general %>% 
  select(species1, animal) %>% 
  set_names('species', 'animal') %>% 
  rbind(
    general %>% 
      select(species2, animal) %>% 
      set_names('species', 'animal')
  ) %>% 
  rbind(
    general %>% 
      select(species3, animal) %>% 
      set_names('species', 'animal')
  ) %>% 
  table() %>% 
  as_tibble() %>% 
  filter(species != 0) %>% 
  filter(species != '')

bacteris_animal %>% 
  filter(n > 0) %>% 
  group_by(animal) %>% 
  summarise(n = n()) %>% 
  mutate(animal = ifelse(animal == 1, 'Dog', 'Cat')) %>% 
  ggplot(aes(x = animal, y = n, fill = animal)) +
  geom_col(colour = 'black', size = 0.15) +
  geom_label(aes(label = n), fill = 'white') +
  xlab('Animal') +
  ylab('N') +
  scale_fill_hp_d(guide = FALSE, begin = 0.3, end = 0.7) +
  ggtitle('Number of Different Bacteria Species per Animal') +
  theme_bw() +
  theme(legend.position = 'none')

gg1 <- bacteris_animal %>% 
  filter(animal == 1) %>% 
  group_by(species) %>% 
  summarise(n = sum(n)) %>% 
  mutate(n =100 * n / sum(n)) %>% 
  ungroup() %>% 
  top_n(10, n) %>% 
  ggplot(aes(x = reorder(species, n), y = n, fill = n)) +
  geom_col() +
  geom_label_repel(aes(label = (n) %>% round(2) %>% paste0('%')), 
             fill = 'white',
             size = 1.5,
             direction = 'x') +
  scale_fill_hp(option = 'HermioneGranger', guide = FALSE) +
  ggtitle('Most Common Bacteria Species in Dogs') +
  coord_flip() +
  xlab('') +
  ylab('(%)') +
  theme_bw()
  
gg2 <- bacteris_animal %>% 
  filter(animal == 2) %>% 
  group_by(species) %>% 
  summarise(n = sum(n)) %>% 
  mutate(n =100 * n / sum(n)) %>% 
    ungroup() %>% 
  top_n(10, n) %>% 
  ggplot(aes(x = reorder(species, n), y = n, fill = n)) +
  geom_col() +
  geom_label_repel(aes(label = (n) %>% round(2) %>% paste0('%')), 
             fill = 'white',
             size = 1.5,
             direction = 'x') +
  scale_fill_hp(guide = FALSE, begin = 0.2, end = 0.6, direction = -1) +
  ggtitle('Most Common Bacteria Species in Cats') +
  coord_flip() +
  xlab('') +
  ylab('(%)') +
  theme_bw()

gg1
gg2
```

## Most Common Bacteria Distribution 
```{r echo = FALSE, warning = FALSE, message = FALSE}
bacteris_animal <- general %>% 
  select(species1, animal) %>% 
  set_names('species', 'animal') %>% 
  rbind(
    general %>% 
      select(species2, animal) %>% 
      set_names('species', 'animal')
  ) %>% 
  rbind(
    general %>% 
      select(species3, animal) %>% 
      set_names('species', 'animal')
  ) %>% 
  table() %>% 
  as_tibble() %>% 
  filter(species != 0) %>% 
  filter(species != '')

bacteris_animal %>% kable()

general %>% 
  select(species1, province, animal) %>% 
    set_names('species', 'province', 'animal') %>% 
    rbind(
      general %>% 
        select(species2, province, animal) %>% 
        set_names('species', 'province', 'animal')
    ) %>% 
    rbind(
      general %>% 
        select(species3, province, animal) %>% 
        set_names('species', 'province', 'animal')
    ) %>% 
    table() %>% 
    as_tibble() %>% 
    filter(species != 0) %>% 
    filter(species != '') %>% 
  group_by(province, animal) %>% 
  mutate(proportion = n / sum(n)) %>% 
  kable()

bacteria_province <- general %>% 
  select(species1, province) %>% 
    set_names('species', 'province') %>% 
    rbind(
      general %>% 
        select(species2, province) %>% 
        set_names('species', 'province')
    ) %>% 
    rbind(
      general %>% 
        select(species3, province) %>% 
        set_names('species', 'province')
    ) %>% 
    table() %>% 
    as_tibble() %>% 
    filter(species != 0) %>% 
    filter(species != '') %>% 
  group_by(province) %>% 
  mutate(n = 100 * n / sum(n))

top_species_dog <- bacteris_animal %>% 
  filter(animal == 1) %>% 
  group_by(species) %>% 
  summarise(c = sum(n)) %>% 
  arrange(-c) %>% 
  top_n(5, c) %>% 
  .$species

top_species_cat <- bacteris_animal %>% 
  filter(animal == 2) %>% 
  group_by(species) %>% 
  summarise(c = sum(n)) %>% 
  arrange(-c) %>% 
  top_n(5, c) %>% 
  .$species
  

bacteria_province %>% 
  filter(species %in% top_species_cat) %>% 
  group_by(province) %>% 
  arrange(-n, .by_group = TRUE) %>% 
  group_by(province) %>% 
  na.omit() %>% 
  right_join(mymap) %>% 
  na.omit() %>% 
  ggplot() +
  geom_polygon(aes( x= long, y = lat, group = group, alpha = n), fill = hp(10)[[4]])  +
  theme_void() +
  scale_alpha_continuous(range = c(0.35,1), name = '%') +
  facet_wrap(.~species) +
  ggtitle('Most Common Bacteria Distribution on Cats')

bacteria_province %>% 
  filter(species %in% top_species_dog) %>% 
  group_by(province) %>% 
  arrange(-n, .by_group = TRUE) %>% 
  group_by(province) %>% 
  na.omit() %>% 
  right_join(mymap) %>% 
  na.omit() %>% 
  ggplot() +
  geom_polygon(aes( x= long, y = lat, group = group, alpha = n), fill = hp(10, option = 'NewtScamander')[[8]])  +
  theme_void() +
  scale_alpha_continuous(range = c(0.35,1), name = '%') +
  facet_wrap(.~species) +
  ggtitle('Most Common Bacteria Distribution on Dogs')
```


## Age Difference

```{r}
general %>% 
  mutate(animal = ifelse(animal == 1, 'Dog', 'Cat')) %>% 
  filter(!is.na(animal)) %>% 
  ggplot(aes(x = infected, y = EDAD, fill = infected)) +
  geom_boxplot(alpha = 1, size = 0.25) +
  facet_wrap(.~animal) +
  scale_fill_hp_d(option = 'sprout', name = 'Culture Result', labels = c('Negative', 'Positive')) +
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  ylab('Age (years)')

general %>% 
  mutate(animal = ifelse(animal == 1, 'Dog', 'Cat')) %>% 
  filter(!is.na(animal)) %>% 
  group_by(animal, infected) %>% 
  summarise(mean_age = mean(EDAD, na.rm = TRUE),
            sd_age   = sd(EDAD,   na.rm = TRUE))


general %>% 
  mutate(animal = ifelse(animal == 1, 'Dog', 'Cat')) %>% 
  filter(!is.na(animal)) %>% 
  group_by(animal) %>% 
  summarise(mean_age = mean(EDAD, na.rm = TRUE),
            sd_age   = sd(EDAD,   na.rm = TRUE))
```

### Dogs Wilcoxon Test

```{r}
x <- general %>% filter(animal == 1) %>%  filter(infected) %>% .$EDAD
y <- general %>% filter(animal == 1) %>% filter(!infected) %>% .$EDAD

wilcox.test(y,x)
```

### Cat Wilcoxon Test

```{r}
x <- general %>% filter(animal == 2) %>%  filter(infected) %>% .$EDAD
y <- general %>% filter(animal == 2) %>% filter(!infected) %>% .$EDAD

wilcox.test(y,x)
```


# Multi-species infection

```{r}
multispecies_dog <- general %>% 
  select(species1, animal, ID) %>% 
  set_names('species', 'animal', 'id') %>% 
  rbind(
    general %>% 
      select(species2, animal, ID) %>% 
      set_names('species', 'animal', 'id')
  ) %>% 
  rbind(
    general %>% 
      select(species3, animal, ID) %>% 
      set_names('species', 'animal', 'id')
  ) %>% 
  filter(animal == 1) %>% 
  filter(species %in% top_species_dog) %>% 
  mutate(id = as.character(id)) %>% 
  filter(species != 0) %>% 
  filter(species != 0) %>% 
  filter(species != '') %>% 
  group_by(id) %>% 
  mutate(n_species = (n() > 1)) %>% 
  group_by(species, n_species) %>% 
  summarise(count = n()) %>% 
  group_by(species) %>% 
  mutate(prop = 100 * count / sum(count)) %>% 
  data.table()

multispecies_cat <- general %>% 
  select(species1, animal, ID) %>% 
  set_names('species', 'animal', 'id') %>% 
  rbind(
    general %>% 
      select(species2, animal, ID) %>% 
      set_names('species', 'animal', 'id')
  ) %>% 
  rbind(
    general %>% 
      select(species3, animal, ID) %>% 
      set_names('species', 'animal', 'id')
  ) %>% 
  filter(animal == 2) %>% 
  filter(species %in% top_species_cat) %>% 
  mutate(id = as.character(id)) %>% 
  filter(species != 0) %>% 
  filter(species != 0) %>% 
  filter(species != '') %>% 
  group_by(id) %>% 
  mutate(n_species = (n() > 1)) %>% 
  group_by(species, n_species) %>% 
  summarise(count = n()) %>% 
  group_by(species) %>% 
  mutate(prop = 100 * count / sum(count)) %>% 
  data.table()

multispecies_cat %>% 
  filter(n_species) %>% 
  ggplot(aes(x = reorder(species, -prop), y = prop)) +
  geom_col(fill = hp(10)[[4]], colour = 'black', size = 0.25) +
  geom_label(aes(label = prop %>% round(2) %>%  paste0(' %'))) +
  xlab('') +
  ylab('%') +
  theme_bw() +
  ggtitle('Proportion of cases in which the Species was not the only one present')

multispecies_dog %>% 
  filter(n_species) %>% 
  ggplot(aes(x = reorder(species, -prop), y = prop)) +
  geom_col(fill = hp(10, option = 'NewtScamander')[[8]], colour = 'black', size = 0.25) +
  geom_label(aes(label = prop %>% round(2) %>%  paste0(' %'))) +
  xlab('') +
  ylab('%') +
  theme_bw() +
  ggtitle('Proportion of cases in which the Species was not the only one present')



multispecies_cat %>% 
  rename(multispecies = n_species) %>% 
  mutate(animal = 'Cat') %>% 
  kable()

multispecies_dog %>% 
  rename(multispecies = n_species) %>% 
  mutate(animal = 'Dog') %>% 
  kable()
```



# Seasonality


## Most Common Bacteria distribued on Seasons
```{r}
bacteria_season <- general %>% 
  select(species1, season, animal) %>% 
  set_names('species', 'season', 'animal') %>% 
  rbind(
    general %>% 
      select(species2, season, animal) %>% 
      set_names('species', 'season', 'animal')
  ) %>% 
  rbind(
    general %>% 
      select(species3, season, animal) %>% 
      set_names('species', 'season', 'animal')
  ) %>% 
  table() %>% 
  as_tibble() %>% 
  filter(species != 0) %>% 
  filter(species != '') %>% 
  group_by(species, animal) %>% 
  mutate(total = sum(n)) %>% 
  data.table()

bacteria_season_all <- general %>% 
  select(species1, season) %>% 
  set_names('species', 'season') %>% 
  rbind(
    general %>% 
      select(species2, season) %>% 
      set_names('species', 'season')
  ) %>% 
  rbind(
    general %>% 
      select(species3, season) %>% 
      set_names('species', 'season')
  ) %>% 
  table() %>% 
  as_tibble() %>% 
  filter(species != 0) %>% 
  filter(species != '') %>% 
  group_by(species) %>% 
  mutate(total = sum(n)) %>% 
  data.table()  


bacteria_season %>% 
  filter(species %in% top_species_dog) %>% 
  filter(animal == 1) %>% 
  filter(season != '') %>% 
  mutate(prop = 100 * n / total) %>% 
  na.omit() %>% 
  mutate(season = factor(season, levels = c('I', 'P', 'V', 'O'))) %>% 
  ggplot(aes(x = season, y = prop)) +
  geom_col(fill = hp(10, option = 'NewtScamander')[[8]], 
           colour = 'black', 
           size = 0.25) +
  geom_label(aes(label = prop %>% round(2) %>% paste0(' %')), size = 2) +
  facet_wrap(.~species) +
  xlab('Season') +
  ylab('(%)') +
  ggtitle('Bacteria Frequency across Seasons on Dogs') +
  theme_bw()
  
bacteria_season %>% 
  filter(animal == 2) %>% 
  filter(species %in% top_species_cat) %>% 
  filter(season != '') %>% 
  mutate(prop = 100 * n / total) %>% 
  na.omit() %>% 
  mutate(season = factor(season, levels = c('I', 'P', 'V', 'O'))) %>% 
  ggplot(aes(x = season, y = prop)) +
  geom_col(fill = hp(10)[[4]], 
           colour = 'black', 
           size = 0.25) +
  geom_label(aes(label = prop %>% round(2) %>% paste0(' %')), size = 2) +
  facet_wrap(.~species) +
  xlab('Season') +
  ylab('(%)') +
  ggtitle('Bacteria Frequency across Seasons on Cats') +
  theme_bw()
  
  
  
  bacteria_season_all %>% 
  filter(species %in% top_species_cat | species %in% top_species_dog) %>% 
  filter(season != '') %>% 
  mutate(prop = 100 * n / total) %>% 
  na.omit() %>% 
  mutate(season = factor(season, levels = c('I', 'P', 'V', 'O'))) %>% 
  ggplot(aes(x = season, y = prop)) +
  geom_col(fill = hp(10, option = 'Gryffindor2')[[8]], 
           colour = 'black', 
           size = 0.25) +
  geom_label(aes(label = prop %>% round(2) %>% paste0(' %')), size = 2) +
  facet_wrap(.~species) +
  xlab('Season') +
  ylab('(%)') +
  ggtitle('Bacteria Frequency across Seasons on All Animals') +
  theme_bw()
  
  
```

### Testing Specific Cases

*Dogs: Enterococcus*

```{r}
bacteria_season %>% 
  filter(animal == 1) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Enterococcus') %>% 
  mutate(this_season = season == 'V') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*Dogs: Escherichia*

```{r}
bacteria_season %>% 
  filter(animal == 1) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Escherichia') %>% 
  mutate(this_season = season == 'P') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*Dogs: Proteus*

```{r}
bacteria_season %>% 
  filter(animal == 1) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Proteus') %>% 
  mutate(this_season = season == 'P') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*Dogs: Staphylococcus*

```{r}
bacteria_season %>% 
  filter(animal == 1) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Staphylococcus') %>% 
  mutate(this_season = season == 'V') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*Dogs: Streptococcus*

```{r}
bacteria_season %>% 
  filter(animal == 1) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Streptococcus') %>% 
  mutate(this_season = season == 'P') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*Cats: Enterococcus (V)*

```{r}
bacteria_season %>% 
  filter(animal == 2) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Enterococcus') %>% 
  mutate(this_season = season == 'V') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*Cats: Escherichia (V)*

```{r}
bacteria_season %>% 
  filter(animal == 2) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Escherichia') %>% 
  mutate(this_season = season == 'V') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*Cats: Proteus (O)*

```{r}
bacteria_season %>% 
  filter(animal == 2) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Proteus') %>% 
  mutate(this_season = season == 'O') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*Cats: Proteus (V)*

```{r}
bacteria_season %>% 
  filter(animal == 2) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Proteus') %>% 
  mutate(this_season = season == 'V') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*Cats: Pseudomonas (O)*

```{r}
bacteria_season %>% 
  filter(animal == 2) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Pseudomonas') %>% 
  mutate(this_season = season == 'O') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*Cats: Proteus (P)*

```{r}
bacteria_season %>% 
  filter(animal == 2) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Proteus') %>% 
  mutate(this_season = season == 'P') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```


*Cats: Staphylococcus (O)*

```{r}
bacteria_season %>% 
  filter(animal == 2) %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Staphylococcus') %>% 
  mutate(this_season = season == 'I') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```


*All: Enterococcus (V)*

```{r}
bacteria_season %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Enterococcus') %>% 
  mutate(this_season = season == 'V') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*All: Escherichia (P)*

```{r}
bacteria_season %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Escherichia') %>% 
  mutate(this_season = season == 'P') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*All: Proteus (P)*

```{r}
bacteria_season %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Proteus') %>% 
  mutate(this_season = season == 'P') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*All: Pseudomonas (O)*

```{r}
bacteria_season %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Pseudomonas') %>% 
  mutate(this_season = season == 'O') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*All: Pseudomonas (I)*

```{r}
bacteria_season %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Pseudomonas') %>% 
  mutate(this_season = season == 'I') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```

*All: Staphylococcus (V)*

```{r}
bacteria_season %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Staphylococcus') %>% 
  mutate(this_season = season == 'V') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```


*All: Streptococcus (V)*

```{r}
bacteria_season %>% 
  mutate(not_this = total - n) %>% 
  filter(season != '') %>% 
  filter(species == 'Streptococcus') %>% 
  mutate(this_season = season == 'P') %>% 
  group_by(this_season) %>% 
  summarise(n = sum(n), not_this = sum(not_this)) %>% 
  chisq.test()
```





# % Positives by Season

```{r}
general %>% 
  filter(season != '') %>% 
  group_by(season, animal) %>% 
  summarise(count = sum(infected),
            proportion = mean(infected)) %>% 
  filter(animal == 2) %>% 
  ggplot(aes(x = season, y = 100 * proportion)) +
  geom_col(fill = hp(10)[[4]], colour = 'black', size = 0.25)  +
  geom_label(aes(label = (proportion*100) %>% round(2) %>% paste0(' %')), fill = 'white') +
  xlab('Season') +
  ylab('(%)') +
  theme_bw() +
  ggtitle('% of Positive Cultures per Season on Cats')

general %>% 
  filter(season != '') %>% 
  group_by(season, animal) %>% 
  summarise(count = sum(infected),
            proportion = mean(infected)) %>% 
  filter(animal == 1) %>% 
  ggplot(aes(x = season, y = 100 * proportion)) +
  geom_col(fill = hp(10, option = 'NewtScamander')[[8]], colour = 'black', size = 0.25)  +
  geom_label(aes(label = (proportion*100) %>% round(2) %>% paste0(' %')), fill = 'white') +
  xlab('Season') +
  ylab('(%)') +
  theme_bw() +
  ggtitle('% of Positive Cultures per Season on Dogs')
```



```{r}
to_test_season <- general %>% 
  filter(season != '') %>% 
  group_by(season, animal) %>% 
  summarise(count = sum(infected)) %>% 
  group_by(animal) %>% 
  mutate(total = sum(count)) %>% 
  ungroup() %>% 
  mutate(no_infected = total - count) %>% 
  mutate(infected = count)



to_test_season %>% 
  filter(animal == 1) %>% 
  select(infected, no_infected, season) %>% 
  mutate(is_summer = season == 'V') %>% 
  group_by(is_summer) %>% 
  summarise(infected = sum(infected),
            no_infected = sum(no_infected)) %>% 
  chisq.test()

to_test_season %>% 
  filter(animal == 2) %>% 
  select(infected, no_infected, season) %>% 
  mutate(is_summer = season == 'V') %>% 
  group_by(is_summer) %>% 
  summarise(infected = sum(infected),
            no_infected = sum(no_infected)) %>% 
  chisq.test()
```

